Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-10 Papers/ms.tex
GL keywords
Slight edits

\begin{keywords}
methods: data analysis --- methods: statistical
\end{keywords}

@@

\citet{2011MNRAS.412.2521B} argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. The source and the lens can be built up from a moderate
number of simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is dark.

@@

\section*{Acknowledgements}
It is a pleasure to thank ...

@@

>>>>

\begin{keywords}
gravitational lensing --- methods: data analysis --- methods: statistical
\end{keywords}

@@

\citet{2011MNRAS.412.2521B} argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models.

The source and the lens can be built up from a mixture of a moderate
number (from a few to a few hundred) of
simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is
dark \citep{2006ApJ...637..608B}.

@@

\section*{Acknowledgements}
It is a pleasure to thank Phil Marshall (Stanford) and Tommaso Treu (UCLA)
for valuable discussion.

@@

\bibitem[\protect\citeauthoryear{Brewer 
\& Lewis}{2006}]{2006ApJ...637..608B} Brewer B.~J., Lewis G.~F., 2006, ApJ, 637, 608
